
\section{Education}

\outerlist{

\entrybig
{\textbf{MSc Digital Audio Engineering} (Distinction)}{\small 2021 \textendash\space 2022}
{University of West London}{}
\innerlist{
\entry{Dissertation entitled "A Time Classification System for ENF Signals" (80\%)} 
\entry{Researched a methodology for time classification of electrical network frequency (ENF) signals using a Siamese neural network of convolutions based on filtered spectral data.}
\entry{Focused learning on C++, Python \& MATLAB competency, alongside digital signal processing, machine learning in audio \& microprocessors (Bela \& Arudino).}
\entry{Modules including Audio Programming, Digital Signal Processing, Mathematics for Programming, Research Methodologies and Machine Learning for Audio.}
}
\entrybig
{\textbf{BA Music} (First Class with Honours)}{\small 2018 \textendash\space 2021}
{University of Plymouth}{}
\innerlist{
\entry{Dissertation entitled "Practical Applications of Machine Learning for Musicians" (70\%)} 
\entry{Awarded for Outstanding Contributions to the Music Department.}
\entry{Focused learning on music theory/history, ethnomusicology, performance, music technology and programming (Python, Max/MSP, Arduino, Adafruit FLORA). Worked with the Wekinator Machine Learning model and various Google Magenta models.}
\entry{Course representative for both the BA and the (newly created) BSc programs. Interviewed by the university as a postgraduate ambassador for the BSc course.}
\entry{Received an unconditional offer from the university for the course.}
}

\entrybig
{\textbf{A Level Mathematics, Music, Psychology, Physics}}{\small 2016 \textendash\space  2018}
{Llandrillo College}{}

\entrybig
{\textbf{9 GCSEs, including Music, English and Mathematics}}{\small 2012 \textendash\space  2016}
{Ruthin School}{}

}