
\section{Relevant Experience}

\outerlist{
\entrybig
	{\textbf{Software Engineer}}{\small November 2023 \textendash\space Present}
	{Native Instruments (iZotope)}{}
\innerlist{
	\entry{C++ Developer: worked on flagship products, implementing new features and fixing bugs in a large/ legacy codebase. Worked closely with product managers, UI/UX designers and QA engineers to deliver high-quality software. Experience with JUCE, Cmajor, Pro Tools AAX, VST3 and Audio Unit plugin formats.}
	\entry{DSP Engineer: Implemented audio DSP algorithms in C++ including filters, oscillators, and effects. Worked closely with senior DSP engineers to ensure high-quality implementations. In charge of updating third party libraries such as Intel's Performance Primatives (IPP) to the latest versions \& providing benchmark reports.}
 	\entry{ML Engineer: Collaborated with the ML research team to integrate machine learning models into audio processing workflows, enhancing product capabilities. Owned deployment of inference engines (ONNXRunTime \& TFLite), as well as auditing the security of ML models loaded from disk.}
	\entry{Javascript: Utilised our webview framework to maintain UIs written in Javascript.}
	\entry{Build engineer: Rotated as monthly build engineer to iZotope, addressing Jenkins build failures and quickly triaging/ escalating active failures.}
	\entry{Python: Kept internal release tooling up to date and added new features to internal QA tools written in Python. Formed a small team to work with Github's REST API to create a PR Status Dashboard, improving cycle times for the company.}
	\entry{Mentor: Mentored senior QAs \& a Junior Engineer, providing guidance on technical and career development. Including DSP basics and build systems.}
}


\entrybig
	{\textbf{Junior Software Engineer}}{\small August 2022 \textendash\space November 2023}
	{Sound Stacks Ltd}{}
\innerlist{
	\entry{Worked on the CMajor compiler, writing tests and improving compiler stability (LLVM).}
	\entry{Maintained the standard DSP library, working with the CTO to write tests \& improve coverage for the library.}
	\entry{Created a proof of concept ML inference engine in CMajor, with a custom Python transpiler.}
	\entry{Deployed the website, including backend APIs and frontend interfaces, ensuring a seamless user experience}
	\entry{Created parts of the VSCode extension to interface with the Cmajor compiler and provide a smooth development experience for users (Graphical UI)}
	\entry{Worked with team on project pitches, planning and execution to deliver high-quality software on time}
}
}